Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-26 paper.tex
Minor change to text

While the relations between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
equation still exists in low-dimensional materials. One important
feature in atomically-thin 2D materials \cite{Novoselov_2016} is that
the electric screening is attenuated and anisotropic
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}. This
makes the empirical relations of dielectric constants in bulk
materials, like the Moss relation invalid within the context of 2D
materials. More critically, the static dielectric constant, a quantity
associated with the macroscopic dielectric and optoelectronic
properties and commonly obtained by theoretical calculations of 2D
materials \cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may
not well describe this microscopic and anisotropic dielectric nature
of 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for a 2D Moss-like relation, which could be used to make predictions
for less-investigated layered crystals and to create materials design
rules at an accurate level.  Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation using highly accurate hybrid functionals and analytical
models, we reveal the long-sought universal dielectric-scale relation
in the 2D world: the in-plane polarizability $\alpha^{\parallel}$ is
inversely proportional to the minimal bandgap $E_{\mathrm{g}}$, while
the out-of-plane polarizability $\alpha^{\perp}$ is directly related
with the intrinsic thickness of 2D materials. An analytical
quantum-mechanical model is developed which give a sound background to
the dielectric-scale relationships. Furthermore, such relations unify
the dielectric properties between the 2D materials and their 3D
counterparts in a natural manner, which ultimately pushes the boundary
of the understanding of electronic screening in both dimensions. The
discovery of scaling relationships between dielectric and electronic
and structural properties in 2D compounds introduces a new and general
pathway for the exploration of their complex physical and chemical
phenomena well beyond the currently possible applications.

>>>>

While the relations between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
equation still exists in low-dimensional materials. One important
feature in atomically-thin 2D materials \cite{Novoselov_2016} is that
the electric screening is attenuated and anisotropic
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}. This
makes the empirical relations of dielectric constants in bulk
materials, like the Moss relation invalid within the context of 2D
materials. More critically, the static dielectric constant, a quantity
associated with the macroscopic dielectric and optoelectronic
properties and commonly obtained by theoretical calculations of 2D
materials \cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may
not well describe this microscopic and anisotropic dielectric nature
of 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for a 2D Moss-like relation, which could be used to make predictions
for less-investigated layered crystals and to create materials design
rules at an accurate level.  Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation using highly accurate hybrid functionals and quantum
mechanical models, we reveal the long-sought universal
dielectric-scale relation in the 2D world: the in-plane polarizability
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while the out-of-plane polarizability
$\alpha^{\perp}$ is directly related with the intrinsic thickness of
2D materials. An analytical quantum-mechanical model is developed
which give a sound background to the dielectric-scale
relationships. Furthermore, such relations unify the dielectric
properties between the 2D materials and their 3D counterparts in a
natural manner, which ultimately pushes the boundary of the
understanding of electronic screening in both dimensions. The
discovery of scaling relationships between dielectric and electronic
and structural properties in 2D compounds introduces a new and general
pathway for the exploration of their complex physical and chemical
phenomena well beyond the currently possible applications.
